Open-Set Domain Adaptation through Self-Supervision

### 2022-02-11 paper/main.tex
fixed student ids

\author{Protopapa Andrea, Quarta Matteo, Ruggeri Giuseppe, Versace Alessandro\\
Politecnico di Torino\\
Italy\\
{\tt\small \{s286302,s292477,s292459,s292477\}@studenti.polito.it <- Riordinare}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

>>>>

\author{Protopapa Andrea, Quarta Matteo, Ruggeri Giuseppe, Versace Alessandro\\
Politecnico di Torino\\
Italy\\
{\tt\small \{s286302,s292477,s292459,292435\}@studenti.polito.it <- Riordinare}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle
